Response to the defense feedback

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{Media and Graphic Libraries}
Recent work also studies side-channel attacks in media and graphic libraries. Gruss et at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library. In the controlled-channel attack~\cite{xu2015controlled}, Xu et al. demonstrate an attack to recover the outline of an image by exploiting the vulnerability in the inverse DCT function in libjpeg. Wang et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries. Their approaches use a machine learning approach to pick cache lines that can be exploited to leak the most information.
\subsubsection*{Others}
Some other side-channel targets also include spelling checking tools and font libraries~\cite{xu2015controlled}. The attack on font libraries is essentially the same as the attack on the graphic library GDK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target operating system kernels. One example is using the side-channel attack to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal the mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR. The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used by a third party to hijack connections between the client and the server~\cite{cao2016off}.

@@

Both hardware~\cite{Page2005PartitionedCA,
    Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
    236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
    brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are difficult to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} use a compiler
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigate side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

@@

\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the sensitive input by observing the execution traces. Therefore, we can conclude the program is vulnerable to side-channel attacks. The method is similar to the UNIX tool \textsf{diff}.  The approach does not need to model or abstract the program's semantics. In general, the approach is quite fast. On the negative side, comparing the trace can find the leakage, but it cannot find the complex relationship between the leakage site and the original secret input. For example, if two leakage sites leak the same information, these approaches cannot find out the two leakages are the same.

@@

\begin{itemize}
    \item Many tools can only analyze the source code or the intermediate representation level. However, side-channel are low-level problems in general.  Most existing tools are research prototypes. For some projects, the tools can only handle the benchmarks in their papers properly. 
    \item These tools heavily rely on SMT solvers. Despite SMT solvers having made incredible progress in performance, SMT solving is still the main bottleneck of these tools. SMT solvers are not good at non-linear arithmetic. However, non-linear arithmetics are quite common in cryptography algorithms.  Recent studies show existing solvers still have bugs when dealing with real number calculations. These calculations are also common in media libraries and machine learning applications.
\end{itemize}

>>>>

\subsubsection*{Media and Graphic Libraries}
Recent work also studies side-channel attacks in media and graphic libraries. Gruss et at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library. In the controlled-channel attack~\cite{xu2015controlled}, Xu et al. demonstrate an attack to recover the outline of an image by exploiting vulnerabilities in the inverse DCT function in libjpeg. Wang et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries. Their approaches use a machine learning approach to pick cache lines that can be exploited to leak the most information.

\subsubsection*{Others}
Some other side-channel targets also include spelling checking tools and font libraries~\cite{xu2015controlled}. The attack on font libraries is essentially the same as the attack on the graphic library GDK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target operating system kernels. One example is using the side-channel attack to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal the mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR. The second example relies on the kernel space side-channel vulnerabilities~\cite{cao2019principled} to infer TCP sequence numbers, which can be used by a third party to hijack connections between a client and a server~\cite{cao2016off}.

@@

Both hardware~\cite{Page2005PartitionedCA,
    Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
    236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
    brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are difficult to adopt. On the contrary, software approaches are
usually easy to implement. Coppens et
al.~\cite{Coppens:2009:PMT:1607723.1608124} develop a compiler extension
to eliminate key-dependent control-flow transfers. Crane et
al.~\cite{crane2015thwarting} mitigate side-channels by randomizing software.
As for crypto libraries, the basic idea is to eliminate key-dependent
control-flow transfers and data accesses. Common approaches include
bit-slicing~\cite{konighofer2008fast,rebeiro2006bitslice} and unifying
control-flows~\cite{Coppens:2009:PMT:1607723.1608124}.

@@

\textbf{Trace comparison.} If a program has two different execution traces under two different sensitive inputs, then attackers can distinguish the two inputs by observing the execution traces. Therefore, we can conclude the program is vulnerable to side-channel attacks. The method is similar to the UNIX tool \textsf{diff}.  The approach does not need to model or abstract the program's semantics. In general, the approach is quite fast. On the negative side, comparing the trace can find the leakage, but it cannot find the complex relationship between the leakage site and the original secret input. For example, if two leakage sites leak the same information, these approaches cannot find out the two leakages are the same.

@@

\begin{itemize}
    \item Many tools can only analyze the source code or the intermediate representation level. However, side-channel are low-level problems in general.  Most existing tools are research prototypes. For some projects, the tools can only handle the benchmarks in their papers properly. 
    \item These tools heavily rely on SMT solvers. Despite SMT solvers having made incredible progress in performance, SMT solving is still the main bottleneck of these tools. SMT solvers are not good at non-linear arithmetic. However, non-linear arithmetics are quite common in cryptography algorithms.  Recent studies show existing solvers still have bugs when dealing with floating number calculations. These calculations are also common in media libraries and machine learning applications.
\end{itemize}
